Large squeezing in Bose-Einstein condensates with large numbers of atoms

### 2013-07-18 large_number_squeezing_with_atoms.tex
Added a reference in the text to the new figure showing that squeezing is possible even when \chi_+ = 0.

In Figure \ref{figTwoModeAnalyticExamples} we plot a solution for the normalised number variance in mode $|a\rangle$ as a function of $\phi$, choosing a typical set of nonlinearities. This example illustrates the basic features of the system: during the final coupling period, the normalised number variance undergoes cyclic variation with a period $\tau=\pi / \Omega$, and has a series of minima. It is necessary to choose both the correct phase $\phi$ as well as the correct length of time for the coupling to be applied in order to obtain optimum squeezing.

@@

\begin{figure}
    \centering
    \includegraphics[width=10cm]{figures/analytic_two_mode_examples.eps}
    \caption{Normalized number variance Var$[N_a]/N_a$ in mode $|a \rangle$ as a function of final recombination time plotted on a logarithmic scale, using four different mixing angles $\phi$. Parameters: $n_a = n_b =5 \times 10^5$, $\chi_{aa}=0.04\, \text{s}^{-1}, \chi_{ab}=0, \chi_{bb}=0.01\,\text{s}^{-1}, \tau_{\mathrm{hold}}=4\times 10^{-4}$s. Solid line, $\phi=0.10$; dash-dotted line, $\phi=1.42$; dashed line, $\phi=3.24$; dotted line, $\phi=4.71$. These particular parameters yield 21\,dB of number squeezing for the $\phi=0.1$ and $\phi=1.42$ cases.} 
    \label{figTwoModeAnalyticExamples}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=10cm]{figures/zero_effective_chi.eps}
    \caption{Relative number squeezing in state $|a\rangle$ (solid line) and number difference squeezing between states $|a\rangle$ and $|b\rangle$ (dashed line) as a function of final recombination time in the case where $\chi_{aa} + \chi_{bb} - 2 \chi_{ab} = 0$. Parameters: $n_a = n_b = 2 \times 10^5$, $\chi_{aa}=0.03\, \text{s}^{-1}, \chi_{ab}=0.02, \chi_{bb}=0.01\,\text{s}^{-1}, \tau_{\mathrm{hold}}=2\times 10^{-3}$s. Solid line, $\phi=1.67$; dashed line, $\phi=1.55$.} 
    \label{figZeroEffectiveChi}
\end{figure}

>>>>

In Figure \ref{figTwoModeAnalyticExamples} we plot a solution for the normalised number variance in mode $|a\rangle$ as a function of $\phi$, choosing a typical set of nonlinearities. This example illustrates the basic features of the system: during the final coupling period, the normalised number variance undergoes cyclic variation with a period $\tau=\pi / \Omega$, and has a series of minima. It is necessary to choose both the correct phase $\phi$ as well as the correct length of time for the coupling to be applied in order to obtain optimum squeezing.  As mentioned previously, squeezing is possible in this system even when the nonlinearity in the reduced Josephson Hamiltonian $\chi_+=\chi_{aa} + \chi_{bb} - 2\chi_{ab} = 0$.  Figure~\ref{figZeroEffectiveChi} demonstrates that significant squeezing is possible in this system if a spin-echo pulse is not used.

@@

\begin{figure}
    \centering
    \includegraphics[width=10cm]{figures/analytic_two_mode_examples.eps}
    \caption{Normalised number variance Var$[N_a]/N_a$ in mode $|a \rangle$ as a function of final recombination time plotted on a logarithmic scale, using four different mixing angles $\phi$. Parameters: $n_a = n_b =5 \times 10^5$, $\chi_{aa}=0.04\, \text{s}^{-1}, \chi_{ab}=0, \chi_{bb}=0.01\,\text{s}^{-1}, \tau_{\mathrm{hold}}=4\times 10^{-4}$s. Solid line, $\phi=0.10$; dash-dotted line, $\phi=1.42$; dashed line, $\phi=3.24$; dotted line, $\phi=4.71$. These particular parameters yield 21\,dB of number squeezing for the $\phi=0.1$ and $\phi=1.42$ cases.} 
    \label{figTwoModeAnalyticExamples}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=10cm]{figures/zero_effective_chi.eps}
    \caption{Relative number squeezing in state $|a\rangle$ (solid line) and number difference squeezing between states $|a\rangle$ and $|b\rangle$ (dashed line) as a function of final recombination time in the case where $\chi_+ = \chi_{aa} + \chi_{bb} - 2 \chi_{ab} = 0$. Parameters: $n_a = n_b = 2 \times 10^5$, $\chi_{aa}=0.03\, \text{s}^{-1}, \chi_{ab}=0.02, \chi_{bb}=0.01\,\text{s}^{-1}, \tau_{\mathrm{hold}}=2\times 10^{-3}$s. Solid line, $\phi=1.67$; dashed line, $\phi=1.55$.} 
    \label{figZeroEffectiveChi}
\end{figure}
